---
title: "Project 1 Task 2"
output: html_document
date: "2022-09-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Function 3

First we create a function called f3, this has four variables that we're going to need. Inside the function there is a equation which is:
f_3(x; s,r,L ) = s + re^{-Lx}. The s variable simply shifts the graph up and down. The r variable stretches vertically. The L variable stethes one end of the graph vertically. In our first graph we have the x variable span from -500 to 500, the s variable is set to 40 so it shifts up 40 units. The r1 variable is 3.5 which stretches the left end of the line vertically up. The L variable is set to 0.005 which this variable also stretches the graph vertically. In our second we only change the r variable to -3.5 which reflects the graph across the x-axis.

$f_3(x; s,r,L ) = s + re^{-Lx}$
```{r f3}
rm(list=ls())
f3 <- function(x, s,r,L){

  
  s + r*exp(-L*x)
}

x <- seq(-500,500)
s <- 40
r1 <- 3.5
L <- .005
y1 <- f3(x, s,r1,L)

par(mfrow=c(1,2),mar=c(2.5,2.5,1,0.25))
plot(x,y1,type='l',xlim=c(-500,500))

r2 <- -3.5
y2 <- f3(x, s,r2,L)

plot(x,y2,type='l',xlim=c(-500,500))
mtext('Changing r in f3', side = 3, line = 0)
```


## Function 5

First off we create a function called f5, this has four variables that we're going to need. Inside the function there is a equation which is: f_5(x; a,b,C) = (a+bx)e^{-Cx}. The a variable shifts the maximum left and up. The b variable decreases the peak and stretches vertically. The C variable compresses in the middle and has the peak shift from the middle to the left. In our first graph we set the x variable to sequence from -500 to 1500. The a variable is set to 25 which sifts the peak up exponentially but sets the y-intercept to 25. The b variable is set to 0.063 which seems to have a reverse effect on the peak from the a variable which then shifts the peak down exponentially. The C variable is set to 0.0024 which stretches the left side of the graph upwards. In the second graph we change the b variable to -0.1 which exponentially increases the left side then plateaus at the x-axis.

$f_5(x; a,b,C) = (a+bx)e^{-Cx}$
```{r f5}
rm(list=ls())
f5 <- function(x, a,b,C){
  
  a+b*x*exp(-C*x)
}

x <- seq(-500,1500)
a <- 25
b1 <- 0.063
C <- 0.0024
y1 <- f5(x, a,b1,C)

par(mfrow=c(1,2),mar=c(2.5,2.5,1,0.25))
plot(x,y1,type='l',xlim=c(-500,1500))

b2 <- -0.1
y2 <- f5(x, a,b2,C)

plot(x,y2,type='l',xlim=c(-500,1500))
mtext('Changing b in f5', side = 3, line = 0)
```